Palmer Archipelago Penguins Data in the palmerpenguins R Package - An Alternative to Anderson's Irises

### 2021-04-27 penguins.Rmd
Reformat PCA figure dimensions, update Python import, add LTER & Gorman citations for data (#22)
* resize PCA figure

* update LTER and Gorman citations for datasets, and change to PyPI palmerpenguins for Python rec

- Adélie penguin data (LTER and Gorman 2020a): [KNB-LTER Data Package 219.5](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.219.5)
- Chinstrap penguin data (LTER and Gorman 2020b): [KNB-LTER Data Package 221.5](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.221.6)
- Gentoo penguin data (LTER and Gorman 2020c): [KNB-LTER Data Package 220.5](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.220.5)

@@

```{r, pca, width = 8, height = 8, fig.cap = "Principal component analysis biplots and screeplots for structural size measurements in penguins (A,C) and iris (B,D), revealing similarities in multivariate patterns, variable loadings, and variance explained by each component. For penguins, variables are flipper length (mm), body mass (g), bill length (mm) and bill depth (mm); groups are visualized by species (Adélie = orange circles, Chinstrap = blue triangles, Gentoo = green squares). For iris, variables are petal length (cm), petal width (cm), sepal length (cm) and sepal width (cm); groups are visualized by species (setosa = light gray circles, versicolor = dark gray triangles, virginica = black squares). Values above screeplot columns (C,D) indicate percent of total variance explained by each of the four principal components.", fig.pos='htbp'}
```

@@

## Other data sources

Python: Python users can access the penguins data in the **seaborn** data visualization library [@michael_waskom_2017_883859]. Example code to load the data in Python:

```
    import seaborn as sns
    df = sns.load_dataset('penguins') 
```

>>>>

- Adélie penguin data [@lter_structural_2020]: [KNB-LTER Data Package 219.5](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.219.5)
- Gentoo penguin data [@lter_structural_2020-1]: [KNB-LTER Data Package 220.5](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.220.5)
- Chinstrap penguin data [@lter_structural_2020-2]: [KNB-LTER Data Package 221.5](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.221.6)

@@

```{r, pca, fig.width = 8, fig.height = 8, fig.cap = "Principal component analysis biplots and screeplots for structural size measurements in penguins (A,C) and iris (B,D), revealing similarities in multivariate patterns, variable loadings, and variance explained by each component. For penguins, variables are flipper length (mm), body mass (g), bill length (mm) and bill depth (mm); groups are visualized by species (Adélie = orange circles, Chinstrap = blue triangles, Gentoo = green squares). For iris, variables are petal length (cm), petal width (cm), sepal length (cm) and sepal width (cm); groups are visualized by species (setosa = light gray circles, versicolor = dark gray triangles, virginica = black squares). Values above screeplot columns (C,D) indicate percent of total variance explained by each of the four principal components.", fig.pos='htbp'}
```

@@

## palmerpenguins for other programming languages

Python: Python users can load the palmerpenguins datasets into their Python environment using the following code to install and access data in the [palmerpenguins Python package](https://pypi.org/project/palmerpenguins/):

```
    pip install palmerpenguins
    from palmerpenguins import load_penguins
    penguins = load_penguins()
```

### 2021-04-27 penguins.tex
Reformat PCA figure dimensions, update Python import, add LTER & Gorman citations for data (#22)
* resize PCA figure

* update LTER and Gorman citations for datasets, and change to PyPI palmerpenguins for Python rec

\begin{itemize}
\tightlist
\item
  Adélie penguin data (LTER and Gorman 2020a):
  \href{https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.219.5}{KNB-LTER
  Data Package 219.5}
\item
  Chinstrap penguin data (LTER and Gorman 2020b):
  \href{https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.221.6}{KNB-LTER
  Data Package 221.5}
\item
  Gentoo penguin data (LTER and Gorman 2020c):
  \href{https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.220.5}{KNB-LTER
  Data Package 220.5}
\end{itemize}

@@

\hypertarget{other-data-sources}{%
\subsection{Other data sources}\label{other-data-sources}}

Python: Python users can access the penguins data in the
\textbf{seaborn} data visualization library
\citep{michael_waskom_2017_883859}. Example code to load the data in
Python:

\begin{verbatim}
    import seaborn as sns
    df = sns.load_dataset('penguins') 
\end{verbatim}

>>>>

\begin{itemize}
\tightlist
\item
  Adélie penguin data \citep{lter_structural_2020}:
  \href{https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.219.5}{KNB-LTER
  Data Package 219.5}
\item
  Gentoo penguin data \citep{lter_structural_2020-1}:
  \href{https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.220.5}{KNB-LTER
  Data Package 220.5}
\item
  Chinstrap penguin data \citep{lter_structural_2020-2}:
  \href{https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.221.6}{KNB-LTER
  Data Package 221.5}
\end{itemize}

@@

\hypertarget{palmerpenguins-for-other-programming-languages}{%
\subsection{palmerpenguins for other programming
languages}\label{palmerpenguins-for-other-programming-languages}}

Python: Python users can load the palmerpenguins datasets into their
Python environment using the following code to install and access data
in the \href{https://pypi.org/project/palmerpenguins/}{palmerpenguins
Python package}:

\begin{verbatim}
    pip install palmerpenguins
    from palmerpenguins import load_penguins
    penguins = load_penguins()
\end{verbatim}
